---
jupyter:
  jupytext:
    formats: ipynb,Rmd
    text_representation:
      extension: .Rmd
      format_name: rmarkdown
      format_version: '1.1'
      jupytext_version: 1.2.4
  kernelspec:
    display_name: Python 3
    language: python
    name: python3
---

# ReadMe

**This is the notebook to import the data from K/I/whatever the driver is and send raw/cleaned data to a postgresql DB on powerplant.**

**Plan:**

1. Read data from db/the same source/maybe the pkl file? 
2. Select down to right TDR measurments
3. Send the raw data from each tdr to DB - this is for examing the suprise values 
4. Clean out missing and stupid high values
5. Average the value in each layer (7 layers in total)
6. Calculate deficit 
7. Upload the calculated deficit to DB - for real irrigation scheduling - need to be a separate table 

**PostgreSQL credentials**

    host = "database.powerplant.pfr.co.nz",
    database = "cflfcl_Rainshelter_SWC",
    user = "cflfcl_Rainshelter_SWC",
    password = "o654UkI6iGNwhzHu"
    
**Format that `sqlalchemy` like**
    
    "postgresql://cflfcl_Rainshelter_SWC:o654UkI6iGNwhzHu@database.powerplant.pfr.co.nz/cflfcl_Rainshelter_SWC"
    
**Demo data source**

    K:\Rainshelter\StonySoilLysimeters


### libraries
```{r connector}
library(reticulate)
```


```{python}
import datetime
import pandas as pd
import numpy as np
import time 
import psycopg2
from sqlalchemy import create_engine
```

```{python}
TestData=pd.read_pickle('FieldData.pkl')
```

```{python}
DataMeans = TestData.loc['2018-10-10':].groupby(level=['Measurement','Depth','Gravels','Stones'],axis=1).mean()
DataMeans =  DataMeans.dropna(axis=1) #For some reason it keeps non valid combinations in so need to extract with this function
DataMeans = DataMeans.resample('4H').last()
#Calculate the water content of the soil profile by multiplying the volumetric water content by each layers
#depth and summing.  The 0-15 layers are divided by 2 to average the two readings
ProfileWater = DataMeans.VolumetricWaterContent.loc[:, 'D1'] * 150 + \
               DataMeans.VolumetricWaterContent.loc[:, 'D2'] * 150 + \
               DataMeans.VolumetricWaterContent.loc[:, 'D3'] * 150 + \
               DataMeans.VolumetricWaterContent.loc[:, 'D4'] * 150 
FieldCapacity = ProfileWater.resample('D').last()
SoilWaterDeficit = -(FieldCapacity - ProfileWater)
```


```{r}
py$FieldCapacity
# py$SoilWaterDeficit
```


