---
jupyter:
  jupytext:
    formats: ipynb,Rmd
    text_representation:
      extension: .Rmd
      format_name: rmarkdown
      format_version: '1.1'
      jupytext_version: 1.2.4
  kernelspec:
    display_name: Python 3
    language: python
    name: python3
---

# ReadMe

**This is the notebook to import the data from K/I/whatever the driver is and send raw/cleaned data to a postgresql DB on powerplant.**

**Plan:**

1. Read data from db/the same source/maybe the pkl file? 
2. Select down to right TDR measurments
3. Send the raw data from each tdr to DB - this is for examing the suprise values 
4. Clean out missing and stupid high values
5. Average the value in each layer (7 layers in total)
6. Calculate deficit 
7. Upload the calculated deficit to DB - for real irrigation scheduling - need to be a separate table 

**PostgreSQL credentials**

    host = "database.powerplant.pfr.co.nz",
    database = "cflfcl_Rainshelter_SWC",
    user = "cflfcl_Rainshelter_SWC",
    password = "o654UkI6iGNwhzHu"
    
**Format that `sqlalchemy` like**
    
    "postgresql://cflfcl_Rainshelter_SWC:o654UkI6iGNwhzHu@database.powerplant.pfr.co.nz/cflfcl_Rainshelter_SWC"
    
**Demo data source**

    K:\Rainshelter\StonySoilLysimeters


### libraries
```{r connector}
library(reticulate)
```


```{python}
import datetime
import pandas as pd
import numpy as np
import time 
import matplotlib.pyplot as plt
import chart_studio.plotly as py
import plotly.tools as tls
import plotly.graph_objs
from sqlalchemy import create_engine
```

## Import the Test pickle data set

_Note_

**ADD** the `pkl` step into the `UpdateDataFrame` function in []()
**However**, write a small `pkl` into the DB before it's overwritten by the automatic update. 
The `.pkl` is an subsetted data set from the raw `.dat`.
It has index already.


Altered the table on web to delete all `NULL`

```
delete from "the_table"
where "date" is null
   or "persons" is null
   or "two_wheelers" is null
   or "cars" is null
   or "vans" is null
   or "buses" is null
   or "autos" is null;
```

```{python}
TestData=pd.read_pickle('FieldData.pkl')
```

```{python}
DataMeans = TestData.loc['2018-10-10':].groupby(level=['Measurement','Depth','Gravels','Stones'],axis=1).mean()
DataMeans =  DataMeans.dropna(axis=1) #For some reason it keeps non valid combinations in so need to extract with this function
DataMeans = DataMeans.resample('4H').last() # 4 hours subsetting

#Calculate the water content of the soil profile by multiplying the volumetric water content by each layers
#depth and summing. 

ProfileWater = DataMeans.VolumetricWaterContent.loc[:, 'D1'] * 150 + \
               DataMeans.VolumetricWaterContent.loc[:, 'D2'] * 150 + \
               DataMeans.VolumetricWaterContent.loc[:, 'D3'] * 150 + \
               DataMeans.VolumetricWaterContent.loc[:, 'D4'] * 150 

# extract the stone and gravel description for renaming
L1 = ProfileWater.columns.get_level_values(0)
L2 = ProfileWater.columns.get_level_values(1)


# rename the columns
ProfileWater.columns = L1 + '_' + L2

FieldCapacity = ProfileWater.resample('D').last()
SoilWaterDeficit = -(FieldCapacity - ProfileWater)
```

```{python}

# FieldCapacity
# SoilWaterDeficit
ProfileWater
```

## Read an initial data set into the DB

```{python}
engine = create_engine("postgresql://cflfcl_Rainshelter_SWC:o654UkI6iGNwhzHu@database.powerplant.pfr.co.nz/cflfcl_Rainshelter_SWC")
SoilWaterDeficit.to_sql(name="SoilWaterDeficit",con=engine,if_exists='replace' ) # will over write db
ProfileWater.to_sql(name="ProfileWater",con=engine,if_exists='replace' ) # will over write db
```


```{r}
library(ggplot2)
library(data.table)
library(dplyr)
swd = as.data.table(py$SoilWaterDeficit, keep.rownames = TRUE )
swd[, rn := lubridate::ymd_hms(rn)] %>% 
  ggplot(aes(rn, Deep_StoneFree)) +
  geom_point() +
  geom_line() +
  theme_classic()
colnames(swd)
```

## A bit plotting for checking

```{python}
SoilWaterDeficit.dropna().plot(figsize=(18,14),style=['r--','b--','g--','r-','b-','g-'], linewidth=4)
plt.ylabel('Soil Water Deficit (mm)', fontsize=36);
plt.tick_params(labelsize=25)
plt.title('Lysimeter stone', fontsize=28);
plt.legend(fontsize=24, loc=4)
plt.show()
```

**Plot shows nothing**
probably too many NAs


```{python}
DailyProfile = ProfileWater.loc[ProfileWater.index.hour == 20,:].resample('D').mean()
DailyProfile.index.name = 'Date'
DailyProfile.plot(figsize=(18,14), linewidth=4)
plt.show()
```



## Problems

1. add new update function 
